---
title: "AssignmentFour"
output: html_document
---

First install all the packages and activate libraries that I need. I also set 
the current directory saved for this R markdown as my working directory. 

```{r setup, echo = TRUE}
library(ggplot2)
library(ggpubr)
library(greekLetters)

mycurrentdirectory = dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(mycurrentdirectory)
```

Then we'll set our variables at y = 7 and foo = 7. And then, i'll plot my starter 
sin plot. 

```{r variables, echo = TRUE}
foo = 7 
y = 7
```
```{r sin, echo=TRUE}
plot(sin)
```

Next, I'm going to making the adjustments needed in the assignment. 

```{r sin2, echo=TRUE}
plot(sin,ylab = expression(tau),xlab=expression(sigma))
```
```{r sin3, echo=TRUE}
plot(sin,ylab = expression(tau),xlab=expression(sigma[s]^2))
```
```{r sin4, echo=TRUE}
plot(sin,ylab = expression(tau),xlab=expression(sigma[s]^2),
     col="red",lty="dotdash",lwd=3)
```
```{r sin5, echo=TRUE}
plot(sin,ylab = expression(tau),xlab=expression(sigma[s]^2),
     col="red",lty="dotdash",lwd=3, cex = 18, main=bquote(Gamma == .(foo)))
```

Finally, i'm going to print it into a 10 inch by 10 inch square with 18 point font. 

```
pdf("plot.pdf",10,10)
plot(sin,ylab = expression(tau),xlab=expression(sigma[s]^2),
     col="red",lty="dotdash",lwd=3, cex = 18, main=bquote(Gamma == .(foo)))
text(0.1, 0.4, bquote(Gamma == .(foo)))
dev.off()
```

Next, i'm going to try this in ggplot2. 

```{r ggplot2setup, echo = TRUE}
library(ggplot2)
data(mtcars)
```
```{r p, echo=TRUE}
p=ggplot(mtcars, aes(x=cyl, y = mpg)) + geom_point()
plot(p)
```

I make the needed adjustments, however, Kevin, my for some reason my geom_text, 
Can't convert the Gamma into actual greek notation. I haven't figured it out yet. 
What would you recommend? 

```{r p1, echo=TRUE}
p1=ggplot(mtcars, aes(x=cyl, y = mpg)) + 
  geom_text(x=6,y=27, label=deparse(bquote(Gamma == .(foo)))) +
  geom_point(color="red",size=3,shape="triangle") + 
  xlab(expression(sigma)) + 
  ylab(expression(tau)) + 
  ggtitle(bquote(Gamma == .(foo)))+
  theme(plot.title = element_text(color="red", face="bold.italic",hjust = 0.5)
              ,text=element_text(size=18))
plot(p1)
```
```{r arranging2, echo= TRUE}
ggarrange(p,p1)
```
```{r arrange2x2, echo = TRUE}
ggarrange(p,p1,p,p1,nrow = 2,ncol = 2)
```

Finally, I plot them as follows: 

```
pdf("ggplot.pdf",10,10)
p1
dev.off()

pdf("ggplot2.pdf",10,10)
ggarrange(p,p1)
dev.off()

pdf("ggplot2by2.pdf",10,10)
ggarrange(p,p1,p,p1,nrow = 2,ncol = 2)
dev.off()

```